---
title: "Chapter 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries


```{r Libraries}
library(rethinking)
library(tidyverse)
library(modelr)


sessionInfo()
```

## Homework 3

### 4E1


$$y_{i} \sim Normal(\mu, \sigma)$$
$$\mu \sim Normal(0,10)$$
$$\sigma \sim Exponential(1)$$
The first line is the likelihood.

### 4E2
Two parameters are in the posterior distribution.

### 4E3

### 4E4

The second line defines the linear model.

### 4E5

Three parameters.

### 4M1

````{r 4M1}

mu <- rnorm(1e4, 0, 10)
sigma <- rexp(1e4, 1)

y <- rnorm(1e4, mu, sigma)

qplot(x=y, geom='density')

````


### 4M2

````{r 4M2}

# flist <- alist(
#  y ~ dnorm(mu, sigma),
#  mu <- dnorm(0, 10),
#  sigma <- dexp(1)
#)

data(Howell1)

d2 <- subset(Howell1, age>=18)


flist <- alist(
  height ~ dnorm(mu, sigma),
  mu <- dnorm(178, 20),
  sigma <- dunif(0, 50)
)

m4.1 <- quap( flist, data=d2 )

precis( m4.1 )

````




### 4M7

Refit the model m4.3, but omit the mean weight xbar this time.

By excluding xbar from the model, the intercept will shift by $\beta$ times $\bar{x}$ (i.e., by 0.9*45).

***Model m4.3 (original version)***

$$h_{i} \sim Normal( \mu_{i}, \sigma)$$
$$u_{i} \sim \alpha + \beta(x_{i} - \bar{x})$$
$$\alpha \sim Normal(178,20)$$
$$\beta \sim LogNormal(0,1)$$
$$\sigma \sim Uniform(0,50)$$
***Model m4.3 (original modified)***

$$h_{i} \sim Normal( \mu_{i}, \sigma)$$
$$u_{i} \sim \alpha + \beta(x_{i})$$



````{r 4M7}

xbar <- mean(d2$weight)

m4.3 <- quap(
  alist(
  height ~ dnorm(mu, sigma),
  mu ~ a + b*( weight - xbar),
  a ~ dnorm( 178, 20 ),
  b ~ dlnorm( 0 , 1),
  sigma <- dunif(0, 50)
  ), data=d2
  )
  

m4.3b <- quap(
  alist(
  height ~ dnorm(mu, sigma),
  mu ~ a + b*( weight ),
  a ~ dnorm( 150, 20 ),
  b ~ dlnorm( 0 , 1),
  sigma <- dunif(0, 50)
  ), data=d2
  )

precis(m4.3)
precis(m4.3b)

  
````



````{r Compare results}

post_orig <- extract.samples( m4.3 )
post_modified <- extract.samples( m4.3b )


d2 <- d2 %>%
  mutate(pred_orig = mean(post_orig$a) + mean(post_orig$b) * ( weight - xbar),
         pred_modified = mean(post_modified$a) + mean(post_modified$b) * ( weight ) )

ggplot(d2, aes(x=weight, y=height)) + geom_point(alpha=0.2) +
  geom_line(aes(x=weight, y=pred_orig), color='red') +
  geom_line(aes(x=weight, y=pred_modified), color='blue') 



pred_tibble <- d2 %>%
 data_grid(weight=weight)

post_orig <- post_orig %>%
  rowid_to_column("draw") 



# Uncertainty of Mu

augment_func_mu <- function(coefs, newdata = pred_tibble) {
  
  predictions <- (coefs$a + coefs$b * (newdata$weight - xbar))
                  
  dplyr::bind_cols(tibble::as_tibble(newdata),
                   tibble::tibble(.fitted = predictions))
}


post_pred_mu <- post_orig[0:100,] %>%
  nest(coefs = c(a, b, sigma)) %>%
  mutate(pred_mu = map(coefs, ~augment_func_mu(.x) ) ) 


post_pred_mu %>%
  unnest(pred_mu) %>%
  ggplot(aes(x=weight, y=.fitted, group=draw)) + geom_line(alpha=0.2) +
  geom_point(inherit.aes = FALSE, data=d2, aes(x=weight, y=height), alpha=0.2)


# Uncertainty of Mu and Sigma


augment_func_overall <- function(coefs, newdata = pred_tibble) {
  
  predictions <- rnorm(length(newdata$weight), coefs$a + coefs$b * (newdata$weight - xbar), coefs$sigma)
                  
  dplyr::bind_cols(tibble::as_tibble(newdata),
                   tibble::tibble(.fitted = predictions))
}



post_pred_overall <- post_orig[0:1000,] %>%
  nest(coefs = c(a, b, sigma)) %>%
  mutate(pred_overall = map(coefs, ~augment_func_overall(.x, newdata = tibble(weight=seq(30,65,1)) ) ) ) 

post_pred_overall %>%
  unnest(pred_overall) %>%
  group_by(weight) %>%
  summarise(lwr = quantile(.fitted, c(0.05)),
            upr = quantile(.fitted, c(0.95)),
            median = quantile(.fitted, c(0.5)) ) %>%
  ggplot(aes(x=weight, y=median, ymin=lwr, ymax=upr)) + geom_line() + geom_ribbon(alpha=0.4) +
  geom_point(inherit.aes = FALSE, data=d2, aes(x=weight, y=height), alpha=0.2) 

````